Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-27 GEMDataSource.Rmd
New data and cleaning
Latest attempt at cleaning 2001-2010 data

# Edit column names for each dataframe
names(Clean01) <- gsub("ki01d01", "2001", names(Clean01))
names(Clean01) <- gsub("country", "Country", names(Clean01))
names(Clean02) <- gsub("ki02d01", "2002", names(Clean02))
names(Clean02) <- gsub("country", "Country", names(Clean02))
names(Clean03) <- gsub("ki03d01", "2003", names(Clean03))
names(Clean03) <- gsub("country", "Country", names(Clean03))
names(Clean04) <- gsub("ki04d01", "2004", names(Clean04))
names(Clean04) <- gsub("ki04ctry", "Country", names(Clean04))
names(Clean05) <- gsub("KI05D01", "2005", names(Clean05))
names(Clean05) <- gsub("KI05ctry", "Country", names(Clean05))
names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
names(Clean06) <- gsub("KI06CTRY", "Country", names(Clean06))
names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
names(Clean07) <- gsub("ki07ctry", "Country", names(Clean07))
names(Clean08) <- gsub("NES08_D01_MEAN", "2008", names(Clean08))
names(Clean08) <- gsub("NES08COUNTRY", "Country", names(Clean08))
names(Clean09) <- gsub("NES09_D01_MEAN", "2009", names(Clean09))
names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
names(Clean10) <- gsub("NES10_D01_MEAN", "2009", names(Clean10))
names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))

@@

# Merge GEMNES country level data
Merged1 <- merge(Clean01, Clean02,
                   union("Country")
                   all = TRUE)

@@

NewData <- Data[myvars, 1]

>>>>

# Edit column names for each dataframe
names(Clean01) <- gsub("ki01d01", "2001", names(Clean01))
names(Clean01) <- gsub("country", "Country", names(Clean01))
names(Clean02) <- gsub("ki02d01", "2002", names(Clean02))
names(Clean02) <- gsub("country", "Country", names(Clean02))
names(Clean03) <- gsub("ki03d01", "2003", names(Clean03))
names(Clean03) <- gsub("country", "Country", names(Clean03))
names(Clean04) <- gsub("ki04d01", "2004", names(Clean04))
names(Clean04) <- gsub("ki04ctry", "Country", names(Clean04))
names(Clean05) <- gsub("KI05D01", "2005", names(Clean05))
names(Clean05) <- gsub("KI05ctry", "Country", names(Clean05))
names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
names(Clean06) <- gsub("KI06CTRY", "Country", names(Clean06))
names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
names(Clean07) <- gsub("ki07ctry", "Country", names(Clean07))
names(Clean08) <- gsub("NES08_D01_MEAN", "2008", names(Clean08))
names(Clean08) <- gsub("NES08COUNTRY", "Country", names(Clean08))
names(Clean09) <- gsub("NES09_D01_MEAN", "2009", names(Clean09))
names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
names(Clean10) <- gsub("NES10_D01_MEAN", "2010", names(Clean10))
names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))

@@

# Merge GEMNES country level data
Merged1 <- merge(Clean01, Clean02, all = TRUE)
Merged2 <- merge(Clean03, Clean04, all = TRUE)
Merged3 <- merge(Clean05, Clean06, all = TRUE)
Merged4 <- merge(Clean07, Clean08, all = TRUE)
Merged5 <- merge(Clean09, Clean10, all = TRUE)
Merged6 <- merge(Merged1, Merged2, all = TRUE)
Merged7 <- merge(Merged3, Merged4, all = TRUE)
Merged8 <- merge(Merged5, Merged6, all = TRUE)
Merged9 <- merge(Merged7, Merged8, all = TRUE)

# Recode countries
Merged9$Country[Merged9$Country == "AUSTRALIA"] <- "Australia"
Merged9$Country[Merged9$Country == "AUSTRIA"] <- "Austria"
Merged9$Country[Merged9$Country == "BELGIUM"] <- "Belgium"
Merged9$Country[Merged9$Country == "CANADA"] <- "Canada"
Merged9$Country[Merged9$Country == "CHILE"] <- "Chile"
Merged9$Country[Merged9$Country == "CZECH REPUBLIC"] <- "Czech Republic"
Merged9$Country[Merged9$Country == "DENMARK"] <- "Denmark"
Merged9$Country[Merged9$Country == "ESTONIA"] <- "Estonia"
Merged9$Country[Merged9$Country == "FINLAND"] <- "Finland"
Merged9$Country[Merged9$Country == "FRANCE"] <- "France"
Merged9$Country[Merged9$Country == "GERMANY"] <- "Germany"
Merged9$Country[Merged9$Country == "GREECE"] <- "Greece"
Merged9$Country[Merged9$Country == "HUNGARY"] <- "Hungary"
Merged9$Country[Merged9$Country == "ICELAND"] <- "Iceland"
Merged9$Country[Merged9$Country == "IRELAND"] <- "Ireland"
Merged9$Country[Merged9$Country == "ISRAEL"] <- "Israel"
Merged9$Country[Merged9$Country == "ITALY"] <- "Italy"
Merged9$Country[Merged9$Country == "JAPAN"] <- "Japan"
Merged9$Country[Merged9$Country == "KOREA"] <- "South Korea"
Merged9$Country[Merged9$Country == "LUXEMBURG"] <- "Luxemburg"
Merged9$Country[Merged9$Country == "MEXICO"] <- "Mexico"
Merged9$Country[Merged9$Country == "NETHERLANDS"] <- "Netherlands"
Merged9$Country[Merged9$Country == "NEW ZEALAND"] <- "New Zealand"
Merged9$Country[Merged9$Country == "NORWAY"] <- "Norway"
Merged9$Country[Merged9$Country == "POLAND"] <- "Poland"
Merged9$Country[Merged9$Country == "PORTUGAL"] <- "Portugal"
Merged9$Country[Merged9$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
Merged9$Country[Merged9$Country == "SLOVENIA"] <- "SLOVENIA"
Merged9$Country[Merged9$Country == "SPAIN"] <- "Spain"
Merged9$Country[Merged9$Country == "SWEDEN"] <- "Sweden"
Merged9$Country[Merged9$Country == "SWITZERLAND"] <- "Switzerland"
Merged9$Country[Merged9$Country == "TURKEY"] <- "Turkey"
Merged9$Country[Merged9$Country == "UNITED KINGDOM"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "UK"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "USA"] <- "United States"
Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"

LongGEM<- melt(data = Merged9,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
names(LongGEM) <- gsub("value", "Support", names(LongGEM))

################### Difficult Section #####################

@@

MYVARS1 <- c("AUSTRALIA", "AUSTRIA", "BELGIUM", "CANADA", "CHILE", "CZECH REPUBLIC", "DENMARK", "ESTONIA", "FINLAND", "FRANCE", "GERMANY", "GREECE", "HUNGARY", "ICELAND", "IRELAND", "ISRAEL", "ITALY", "JAPAN", "KOREA", "LUXEMBURG", "MEXICO", "NETHERLANDS", "NEW ZEALAND", "NORWAY", "POLAND", "PORTUGAL", "SLOVAK REPUBLIC", "SLOVENIA", "SPAIN", "SWEDEN", "SWITZERLAND", "TURKEY", "UNITED KINGDOM", "UNITED STATES")

Long2[,"Support"] <- as.numeric(Long2[,"Support"])
Long2[,"Year"] <- as.numeric(Long2[,"Year"])
Long2[,"Country"] <- as.factor(Long2[,"Country"])

Long2

Long2[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"), ]

# Grab only countries we need
NewData <- Long2[rownames = myvars, 
                 colnames = mystats]

mystats <- c("Country", "Year", "Support")

NewData1 <- data.frame(NewData)
